Fourmile Calibrations and Output

### 2025-12-14 fourmile_output_dec2024.Rmd
updating filepaths

# export
ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids.png',
       dpi=600,
       width = 12,
       height = 8)

@@

flow <- read_csv('./discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date)) %>%
  drop_na()

>>>>

# export
ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids_oct2025.png',
       dpi=600,
       width = 12,
       height = 8)

@@

flow <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date)) %>%
  drop_na()
